\begin{document}
\employer{Los Alamos National Laboratory}
\location{Los Alamos, NM}
\datestart{Aug 2017}
\dateend{Present}
\jobtitle{Post-baccalaureate Intern}
\duration{11+ months}
\accomplishment{Continued research into whether commercial virtual reality headsets can be applied to scientific data analysis and visualization.}
\accomplishment{Contributed to the design of the upcoming Viewmaster III HPC visualization cluster.}
\accomplishment{Administering both the system and network sides of a massively heterogeneous cluster (Darwin) with 330+ nodes and 60+ hardware configurations, including x86_64, PowerPC 64 LE, and ARM architectures.}
\accomplishment{Performing as the primary administrator and maintainer for the GitLab CE instance at gitlab.lanl.gov.}
\accomplishment{Serving as a co-chair for the Student Worker Safety & Security Team.}

\employer{Los Alamos National Laboratory}
\location{Los Alamos, NM}
\datestart{Jun 2017}
\dateend{Aug 2017}
\jobtitle{Computer System, Cluster and Network Summer Institute Intern}
\duration{3 months}
\accomplishment{Worked with a small team to build and configure a small-scale cluster using CentOS 6 and 7.}
\accomplishment{Gained knowledge of services such as DHCP, iptables/firewalld, NFS, NTP, DNS, LDAP, SSH, TFTP, PXE.}
\accomplishment{Working with Intel’s Omni-Path Architecture researching fabric congestion, specifically its causes and its effect on performance. (Poster: LA-UR-17-27041)}

\employer{Los Alamos National Laboratory}
\location{Los Alamos, NM}
\datestart{May 2016}
\dateend{Aug 2016}
\jobtitle{Undergraduate Summer Intern}
\duration{4 months}
\accomplishment{Researched whether the then-newly-released commercial virtual reality headsets could be applied to scientific data analysis and visualization. (Poster: LA-UR-16-25368)}

\employer{Indiana University South Bend}
\location{South Bend, IN}
\datestart{Oct 2014}
\dateend{Oct 2015}
\jobtitle{Computer Science Tutor}
\duration{1 year}
\accomplishment{Explained basic computer science theory and programming methodologies to other students.}
\accomplishment{Helped to troubleshoot students’ code to find bugs and to help optimize their code to run more efficiently.}

\employer{Towne Air Freight}
\location{South Bend, IN}
\datestart{Nov 2012}
\dateend{Jun 2013}
\jobtitle{Level 1 Support Technician}
\duration{8 months}
\accomplishment{Performed as the primary point of contact for over 1000 internal customers and all external customers for quickly resolving low level technical issues.}

\employer{United States Marine Corps}
\location{Camp Lejeune, NC}
\datestart{Nov 2007}
\dateend{Nov 2012}
\jobtitle{Electronics Maintenance Technician/Supervisor, Non-Commissioned Officer}
\duration{5 years}
\accomplishment{Maintained multiple million dollars’ worth of terrestrial and satellite communications systems.}
\accomplishment{Oversaw the work of up to 5 subordinates at any given time.}
\accomplishment{Managed deployed armory for battalion while in Afghanistan, including 200+ personal and crew-served weapons and optic systems at 8 different physical locations throughout the country and established a regularly scheduled maintenance cycle.}
\accomplishment{Awarded a Navy and Marine Corps Achievement Medal for performance in Afghanistan.}
\accomplishment{Created a system to dynamically track ammunition expenditures by battalion troops.}

\employer{Towne Air Freight}
\location{South Bend, IN}
\datestart{Jun 2003}
\dateend{Nov 2007}
\jobtitle{Desktop Administrator}
\duration{4 years, 5 months}
\accomplishment{Performed all non-server computer maintenance for over 1000 internal customers.}
\accomplishment{Administered entire inventory of Wyse thin terminals, including creating and deploying customized OS images as well as any and all hardware replacements needed.}
\accomplishment{Managed fleet of cell phones used by drivers to remotely enter Proof of Delivery into the system.}
\end{document}
